% -*- latex -*-

\input{mymacs}
\newcommand{\unfinished}{\par\textbf{Unfinished !!!!!!!!!!!!!}}

\usepackage{subfig}
\usepackage[metapost]{mfpic}
\opengraphsfile{myfigs}


\title{Notes and Solutions to Exercises \\
          from \\
       Real and Complex Analysis / Walter Rudin}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\maketitle
\newpage
\tableofcontents
\newpage


\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setcounter{chapter}{-2}
\chapterTypeout{About this Document}

Here I try to solve problems
from the book \cite{RudinRCA80}
\begin{center}
\textbf{Real and Complex Analysis}\\
by
\textbf{Walter Rudin}

Whenever there is reference to theorem or lemma, it implicitly
targets this text, unless otherwise specified.
Furthermore, we have in this document lemmas or theorems
which are referred to as \emph{local} lemma
or \emph{local} theorem.
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Notation}

\input{notations}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapterTypeout{Prologue: The Exponential Function}

\input{trig}

\iftrue
 \input{rudinrca1}
 \input{rudinrca2}
 \input{rudinrca3}
 \input{rudinrca4}
 \input{rudinrca5}
 \input{rudinrca6}
 \input{rudinrca7}
 \input{rudinrca8}
 \input{rudinrca9}
 \input{rudinrca10}
 \input{rudinrca11}
\else
 % \setcounter{chapter}{0}  \input{rudinrca1}
 % \setcounter{chapter}{1}  \input{rudinrca2}
 % \setcounter{chapter}{2}  \input{rudinrca3}
 % \setcounter{chapter}{3}  \input{rudinrca4}
 \setcounter{chapter}{4}  \input{rudinrca5}
 % \setcounter{chapter}{5}  \input{rudinrca6}
 % \setcounter{chapter}{6}  \input{rudinrca7}
 % \setcounter{chapter}{7}  \input{rudinrca8}
 % \setcounter{chapter}{8}  \input{rudinrca9}
 \setcounter{chapter}{9}  \input{rudinrca10}
 \setcounter{chapter}{10}  \input{rudinrca11}
\fi



\iffalse
\setcounter{chapter}{10}
\input{rudinrca11}
\input{rudinrca12}
\fi


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\chapterTypeout{Hausdorff's Maximality Theorem}

\index{Hausdorff}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\index{Zorn}
\section{Equivalence of Zorn Lemma}

We recall the definition of a \emph{chain}

Given a partially ordered set $X$, a subset \(A\subset X\) is a chain
if the inherited order is a total order.

Let's state Zorn's lemma.
\begin{llem}
Let $X$ be a partially ordered set. If each chain in $X$ has an upper bound
in $X$, then $X$ has a maximal element.
\end{llem}

This is similar to Hausdorff's maximality theorem.
Let's state it and prove it rigorously.

\begin{llem}
Let $X$ be a partially ordered set.
% The following statements are equivalent
\begin{itemize}
 \item[(\textbf{H})]
 If $X$ be a partially ordered set then there exists a maximal chain.
 \item[(\textbf{Z})]
 If $X$ be a partially ordered set and for every chain \(C\subset X\)
 there exists \(b\in X\) such that \(x\leq b\) for all \(x\in C\).
\end{itemize}
\end{llem}
\begin{thmproof}
Assume (\textbf{H}) is true.
Let $X$ be a partially ordered set such that every chain \(C\subset X\)
has a upper bound \(b\in X\). By (\textbf{H}) there exists a maximal chain
\(C_M\). Let $b$ be an upper bound of \(C_m\). If by negation
$b$ is not a maximal element of $X$ then there exists \(u\in X\)
such that \(b<u\), but then \(C_m \subsetneq C_m \cup \{u\}\)
and both are chains, contradiction to the maximality of \(C_m\).
Thus $b$ is a maximal element in $X$.

Conversely, assume (\textbf{Z}) is true. Let $X$ be a partially ordered set.
Let \frakC\ be the family of chains in $X$.
Order the (chain) elements of \frakC\ by inclusion.
For each chain \(c \in \frakC\),
(chain of chains) its union \(u = \cup c\) is also a chain and is
an upper bound of $c$. Thus the assumption of (\textbf{Z}) hold
for \frakC\ (as $X$)
and hence there is a maximal element \(C_M\in\frakC\) which is a maximal chain.
\end{thmproof}

The (\textbf{H}) statement may be viewed as stronger since
when showing (\textbf{Z}) we stayed with the same $X$.
While when showing the converse, we needed to apply $X$
on \(\frakC\subset P(X)\).


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \bibliographystyle{plain}
\bibliographystyle{alpha}
\bibliography{rudinrca}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\printindex


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\closegraphsfile
\end{document}

