%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapterTypeout{Banach Algebras}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Notes} % 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Proof of Theorem~10.13}

The proof defines \(f(\lambda) = (\lambda e - x)^{-1}\)
and for \(\|x\|< |\lambda |\) claims that
\(f(\lambda) = \sum_{n=0}^\infty \lambda^{-n-1} x^n\).
To show it, define \(S = \sum_{n=0}^\infty \lambda^{-n-1} x^n\).
Now \(S = (e/\lambda) \sum_{n=0}^\infty (x/\lambda)^n\).
Clearly \(S - (x/\lambda)S = e/\lambda\) and so 
\begin{equation*}
S
= e \cdot \left(\lambda(e - (x/\lambda))\right)^{-1}
= e \cdot (\lambda e - x)^{-1} = f(\lambda).
\end{equation*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Proof of Theorem~10.24}

The proof says that when \(\lambda \notin \sigma(x)\), then
\begin{equation*}
(\lambda e -x)^{-1}
= (\alpha e -x)^{-1}
  + (\alpha - \lambda)(\alpha  e -x)^{-1}(\lambda e -x)^{-1}.
\end{equation*}

Multiply by \((\alpha  e -x)(\lambda e -x)\) we get
an equivalent equality which is trivially true.
\begin{equation*}
\alpha  e -x = (\lambda e -x) + (\alpha - \lambda)e.
\end{equation*}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{On Section 10.26 Comments}

In comment \ich{c} of Section~10.26 the text claims
\(\tilde{f}(\alpha e) = f(\alpha)e\). To show it
\begin{equation*}
\tilde{f}(\alpha e)
  = \frac{1}{2\pi i}\int_{\Gamma} f(\lambda)(\lambda e - \alpha e)^{-1} d\lambda
  = \frac{1}{2\pi i}\int_{\Gamma} \frac{f(\lambda)e}{\lambda \alpha} d\lambda
  = \frac{1}{2\pi i}
    \left(\int_{\Gamma} \frac{f(\lambda)}{\lambda \alpha} d\lambda\right)e
  = f(\alpha)e.
\end{equation*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Proof of Theorem 10.28}

The proof of Theorem~10.28 claims that if
\(f\in H(\Omega)\) and \(f(\alpha)=0\)
then there exists \(h\in H(\Omega)\) such that
\((\lambda - \alpha)h(\lambda) = f(\lambda)\) where \(\lambda\in\Omega\).

Looking at
\begin{equation*}
\lim_{\lambda\to\alpha} \frac{f(\lambda)}{\lambda - \alpha}
= \lim_{\lambda\to\alpha} \frac{f(\lambda) - f(\alpha)}{\lambda - \alpha}
= f'(\alpha).
\end{equation*}
So for \(\lambda\in \Omega\) we can define
\begin{equation*}
h(\lambda) = \left\{
\begin{array}{ll}
 f(\lambda)/(\lambda - \alpha) & \textnormal{if}\;\lambda \neq \alpha \\
 f'(\alpha) &                    \textnormal{if}\;\lambda = \alpha \\
\end{array}
\right.
\end{equation*}
Clearly \(h\in H(\Omega\setminus\{\alpha\})\) and continuous on \(\Omega\).
By Theorem~10.20 of \cite{RudinRCA80} \(h\in H(\Omega)\).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Exercises} % pages 271-274

Throughout this set of exercises,
$A$ denotes a Banach algebra and \(x, y, \ldots\) denote
elements of $A$, unless the contrary is stated.

%%%%%%%%%%%%%%%%%
\begin{enumerate}
%%%%%%%%%%%%%%%%%

%%%%%%% 1
\begin{excopy}
Use the identity \((xy)^n = x(yx)^{n-1}y\) to prove that \(xy\) and \(yx\)
always have the same spectral radius.
\end{excopy}

\begin{align*}
 \rho(xy) &= \lim_{n\to\infty} \|(xy)^n\|^{1/n} = \lim_{n\to\infty}\|x(yx)^{n-1}y\|^{1/n} \\
  &\leq \lim_{n\to\infty} \left(\|x\|\cdot \|(yx)^{n-1}\|\cdot \|y\|\right)^{1/n} \\
  &= \left(\lim_{n\to\infty} \|x\|^{1/n}\right)
     \cdot
     \left(\lim_{n\to\infty} \|(yx)^{n-1}\|^{1/n}\right)
     \cdot
     \left(\lim_{n\to\infty} \|y\|^{1/n}\right) \\
  &= 1 \cdot \left(\lim_{n\to\infty} \|(yx)^{n-1}\|^{1/n}\right) \cdot 1
   = \lim_{n\to\infty} \|(yx)^{n-1}\|^{1/n} \\
  &= \lim_{n\to\infty} \left(\|(yx)^{n-1}\|^{1/(n-1)}\right)^{n/n-1} \\
  &= \lim_{n\to\infty} \left(\rho(yx)\right)^{n/(n-1)} = \rho(yx)
\end{align*}

%%%%%%% 2
\begin{excopy}
\begin{itemize}
  \itemch{a}
    If $x$ and \(xy\) are invertible in $A$, prove that $y$ is invertible.
  \itemch{b}
    If \(xy\) and \(yx\) are invertible in $A$,
    prove that $x$ and $y$ are invertible. (The
    commutative case of this was tacitly used in the proofs of Theorems~10.13
    and 10.28.)
  \itemch{c}
    Show that it is possible to have \(xy = e\) but \(yx \neq e\).
    For example, consider the
    right and left shifts \(S_R\), and \(S_L\),
    defined on some Banach space of functions $f$
    on the nonnegative integers by
    \begin{align*}
     (S_R f)(n) &= f(n - 1) \qquad \textnormal{if}\quad n \geq 1,\\
     (S_R f)(0) &= 0, \\
     (S_L f)(0) &= f(n + 1) \qquad \textnormal{for all}\quad n \geq 0.
    \end{align*}
  \itemch{d}
    If \(xy = e\) and \(yx = z \neq e\),
    show that $z$ is a nontrivial idempotent. (This
    means that \(z^2 = z\), \(z \neq 0\), \(z \neq e\).)
\end{itemize}
\end{excopy}

\begin{itemize}
  \itemch{a}
    Let \(z = (xy)^{-1} x\). Now using associativity
    \begin{equation*}
      zy = ((xy)^{-1} x)y = (xy)^{-1}(xy) = e
    \end{equation*}
    and 
    \begin{align*}
      yz &= y((xy)^{-1} x) = (x^{-1} x)(y((xy)^{-1} x) = x^{-1}(xy)(xy)^{-1} x \\
         &= x^{-1}((xy)(xy)^{-1})x = x^{-1}ex = e.
    \end{align*}
    Hence \(z = y^{-1}\).
  \itemch{b}
    We have two sides ``inverses'':
    \(((yx)^{-1}y)\cdot x = e\)
    and
    \(x\cdot(y(xy)^{-1}) = e\).
    Put \(a = (yx)^{-1}y\) and \(b = y(xy)^{-1}\)
    so \(ax = xb = e\). Now
    \(a = a(xb) = (ax)b = b\)
    Thus \(x^{-1} = a = b\).
    By symmetry $y$ is invertible as well.
  \itemch{c}
    Indeed \(S_L\cdot S_R = e\) but \(S_R\cdot S_L \neq e\).
  \itemch{d}
    Showing idempotent: \(z^2 = (yx)(yx) = y(xy)x = yex = yx = z\).
    If by negation \(z=0\) then \(e = xy = x(yx)y = 0\) contradiction.
\end{itemize}

%%%%%%% 3
\begin{excopy}
Prove that every finite-dimensional $A$ is isomorphic to an algebra of matrices.
\emph{Hint}:
The proof of Theorem~10.2 shows that every $A$ is isomorphic to
a sub-algebra of \(\scrB(A)\).
Conclude that \(xy = e\) implies \(yx = e\) if \(\dim A < \infty\).
\end{excopy}

Let \seq{a}{n} be a base for $A$.
Using the unique linear combination of the base,
let \(\beta: A \to \C^n\) defined such that
\begin{equation*}
 \forall x\in A, \qquad
 x = \sum\nolimits_{j=1}^n \left(\beta(x)\right)_j a_j.
\end{equation*}
Clearly \(\beta\) is a linear operator.
Any operator in \(\scrB(A)\) is determined by its action on the base.
\iffalse
For any \(j,k\in\N_n\) let \(b_{j,k}\) be defined such that
\begin{equation*}
a_j\cdot a_k = \sum\nolimits_{k=1}^n b_{j,k} a_k.
\end{equation*}
\fi
Let \(\rho,x \in A\), and \(\rho\cdot x = y\).
Let see how \(\beta(x)\) is \(\rho\)-mapped to \(\beta(y)\).
\begin{equation*}
\rho\cdot x =
  \left(\sum\nolimits_{j=1}^n \left(\beta(\rho)\right)_j a_j\right)
  \cdot
  \left(\sum\nolimits_{j=1}^n \left(\beta(x)\right)_j a_j\right)
  =
  \left(\sum\nolimits_{j=1}^n \left(\beta(y)\right)_j a_j\right)
\end{equation*}
Let \(r_{j,k} = \left(\beta(\rho(a_j)\right)_k\) where \(j,k\in\N_n\).
Let \(R_\rho = (r_{j,k})_{j,k=1}^n\) be a \(n\times n\) matrix.
we need to show the following equality in \(\C^n\)
\begin{equation*}
R_\rho\cdot \beta(x) = \beta(y).
\end{equation*}
By linearity, it is sufficient to show the equality for \(x=a_j\).
For each \(k\in\N_n\)
\begin{equation*}
\left(R_\rho\cdot \beta(a_j) \right)_k = r_{j,k}.
\end{equation*}
Thus we have an isomorphism \(A \leftrightarrow \C^{n^2}\).
From the theory of matrices, we know that a matrix $M$ is
invertible iff \(\det(M)\neq 0\).

Now say the isomorphism maps \(x\to M_1\) and \(y\to M_2\).
If \(M_1\times M_2 = I_n\) as \(n\times n\) matrices,
then \(\det(M_1) \neq 0 \neq \det(M_2)\).
Thus both matrices are invertible, the inverse is unique
and so  \(M_2\times M_1 = I_n\) as well.
So if \(xy=e\) then \(yx=e\).

%%%%%%% 4
\begin{excopy}
\begin{itemize}
\itemch{a}
Prove that \(e - yx\) is invertible in $A$
if \(e - xy\) is invertible. \emph{Suggestion:} Put
\(z =(e-xy)^{-1}\), write $z$ as a geometric series
(assume \(\|x\| < 1\), \(\|y\| < 1\)), and
use the identity stated in Exercise~1
to obtain a finite formula for \((e - yx)^{-1}\)
in terms of $x$, $y$, $z$. Then show that this formula works without any
restrictions on \(\|x\|\) or \(\|y\|\).
\itemch{b}
If \(\lambda \in \C\) \(\lambda \neq 0\),
  and \(\lambda \in \sigma(xy)\), prove that \(\lambda \in \sigma(yx)\).
  Thus \(\sigma(xy) \cup \{0\} = \sigma(yx) \cup \{0\}\).
  Show, however, that \(\sigma(xy)\) is not always equal to \(\sigma(yx)\).
\end{itemize}
\end{excopy}

\begin{itemize}
\itemch{a}
As geometric series
\begin{equation*}
z = \sum\nolimits_{k=0}^\infty (xy)^k
\end{equation*}
Now
\begin{equation*}
yzx
= \sum\nolimits_{k=0}^\infty y(xy)^kx
= \sum\nolimits_{k=1}^\infty (yx)^k
\end{equation*}
so as a conjecture
\begin{equation} \label{eq:conj:inv:emyx}
e + yzx = \sum\nolimits_{k=0}^\infty (yx)^k = (e - yx)^{-1}.
\end{equation}
Checking from left
\begin{align*}
(e + yzx)\cdot(e - yx)
 &= e - yx + yzx - yzxyx
  = e + y(z - zxy - e)x \\
 &= e + y(z(e - xy) - e)x 
  = e + y\cdot 0\cdot x = e
\end{align*}
and checking from right
\begin{align*}
(e - yx)\cdot(e + yzx)
 &= e + yzx - yx - yxyzx = e + y(z - xyz - e)x \\
 &= e + y((e - xy)z - e)x
    = e + e\cdot 0\cdot x = e
\end{align*}
So the \eqref{eq:conj:inv:emyx} conjecture holds.
\itemch{b}
Let \(\mu = \lambda^{-1}\).
Note that \(\mu (xy) = (\mu x)y = x(\mu y)\)
and \(\mu (yx) = (\mu y)x = y(\mu x)\).
By assumption \(xy -\lambda e\) is not invertible
and so \(\mu xy - e\) is not invertible.
By \ich{a} \(\mu yx - e\) is not invertible
and so \(yx - \lambda e\) is not invertible. Thus \(\lambda \in \sigma(yx)\).

Using exercise~2.\ich{c},
We have \(S_L\cdot S_R = e\) and \(S_R\cdot S_L \neq e\)
and for any \(x\in\ell^p\) we have \(((S_R\cdot S_L)(x))(0) = 0\)
which shows that \(S_R\cdot S_L\) is not invertible.
Thus \(0 \in \sigma(S_R\cdot S_L) \setminus  \sigma(S_L\cdot S_R) \),
and \(\sigma(S_R\cdot S_L) \neq  \sigma(S_L\cdot S_R)\).
\end{itemize}

%%%%%%% 5
\begin{excopy}
Let \(A_0\) and \(A_1\),
be the algebras of all complex 2-by-2 matrices of the form

\begin{equation*}
\left(
  \begin{array}{ll}
   \alpha & 0 \\
   0 & \beta
  \end{array}
\right),
\qquad
\left(
  \begin{array}{ll}
   \alpha & \beta \\
   0 & \alpha
  \end{array}
\right).
\end{equation*}
Prove that every two-dimensional complex algebra $A$ with unit $e$ is isomorphic
to one of these
  and that \(A_0\) is not isomorphic to \(A_1\).
    \emph{Hint:} Show that $A$ has a
basis \(\{e, a\}\) in which \(a^2 = \lambda e\) for some \(\lambda \in \C\).
  Distinguish between the cases
  \(\lambda=0\), \(\lambda \neq 0\).
  Show that there exists a three-dimensional noncommutative
Banach algebra.
\end{excopy}

We have \(a\in A_0\) such that \(\{I, a\}\) is a base and
\(a^2 = \lambda e\) with \(\lambda \neq 0\).
for example: \(a = \left(
\begin{smallmatrix}
1 & 0 \\
0 & -1
\end{smallmatrix}
\right)\).
But by negation if we have such an \(a\in A_1\) we would have
\begin{equation*}
a^2 =
\left(
\begin{array}{ll}
\alpha & \beta \\
0 & \alpha \\
\end{array}\right)^2 =
\left(
\begin{array}{ll}
\alpha^2 & 2\alpha\beta \\
0 & \alpha^2 \\
\end{array}\right) = \lambda I
\end{equation*}
But then \(\alpha=0\) or \(\beta=0\) and in both cases \(\{I, a\}\)
would not span $A$, contradicting the base assumption.
This \(A_0\) and \(A_1\) are not isomorphic.

Let \(\{e, b\}\) be an arbitrary base for 2-dimensional $A$.
Look at a linear combination \(b^2 = \alpha e + \beta b\)
where \(\alpha,\beta \in \C\).
Consider
\((b + ze)^2 = (\alpha + z^2) e + (\beta + 2z)b\),
so we pick \(z = -\beta/2\), \(a = b + ze\) and \(\lambda = \alpha + z^2\)
so we have (as the hint) a base \(\{e, a\}\) and \(a^2 = \lambda e\).
If \(\lambda \neq 0\) we have isomorphism with \(A_0\)
\begin{equation*}
  \alpha e + \beta a \to
  \left(
  \begin{array}{ll}
  \alpha + \beta & 0 \\
  0 & \alpha - \beta
  \end{array}
  \right).
\end{equation*}
If \(\lambda = 0\) we have isomorphism with \(A_1\)
\begin{equation*}
  \alpha e + \beta a \to
  \left(
  \begin{array}{ll}
  \alpha & \beta \\
  0 & \alpha
  \end{array}
  \right).
\end{equation*}

Look at the $3$-dimensional algebra of the \(2\times 2\)
complex matrices of the form
\(\left(
\begin{smallmatrix}
\alpha & \beta \\
0 & \gamma
\end{smallmatrix}
\right)\).
Now
\begin{equation*}
\left(
  \begin{array}{ll}
   \alpha_1 & \beta_1 \\
   0 & \gamma_1
  \end{array}
\right)
\cdot
\left(
  \begin{array}{ll}
   \alpha_2 & \beta_2 \\
   0 & \gamma_2
  \end{array}
\right)
=
\left(
  \begin{array}{ll}
   \alpha_1\alpha_2 & \alpha_1\beta_2 + \beta_1\gamma_2 \\
   0 & \gamma_1\gamma_2
  \end{array}
\right).
\end{equation*}
and
\begin{equation*}
\left(
  \begin{array}{ll}
   \alpha_2 & \beta_2 \\
   0 & \gamma_2
  \end{array}
\right)
\cdot
\left(
  \begin{array}{ll}
   \alpha_1 & \beta_1 \\
   0 & \gamma_1
  \end{array}
\right)
=
\left(
  \begin{array}{ll}
   \alpha_2\alpha_1 & \alpha_2\beta_1 + \beta_2\gamma_1 \\
   0 & \gamma_2\gamma_1
  \end{array}
\right).
\end{equation*}
So if we pick \(\alpha_1 = \alpha_2 = \beta_1 = \gamma_2 = 0\)
and \(\beta_2 = \gamma_1 = 1\) we see that this algebra is noncommutative.

%%%%%%% 6
\begin{excopy}
Let $A$ be the algebra of all complex functions $f$ on
\(\{1, 2, 3, \ldots\}\) which are $0$
except at finitely many points, with pointwise addition and multiplication and
norm
\begin{equation*}
 \|f\| = \sum\nolimits_{k=1}^\infty k^{-2}|f(k)|.
\end{equation*}
Show that multiplication is left-continuous
  (hence also right-continuous, since $A$
is commutative) but not jointly continuous. (Adjunction of a unit element, as
suggested in Section~10.1, would make no difference.)
  Show, in fact, that there is
a~sequence \(\{f_n\}\) in $A$ so that \(\|f_n\| \to 0\)
  but \(\|f_n^2\| \to \infty\), as \(n \to \infty\).
\end{excopy}

The continuity of single side is trivial
since in the limit of
\(\lim_{n\to\infty} f_n\cdot g\)
or
\(\lim_{n\to\infty} g\cdot f_n\)
the g function is constant
and the formal infinite sum is actually a finite sum,
since $g$ is $0$ except or finite set of points.
The finite sum of limits is clearly the limit of the sums.

Let \(h(n) = (1/\left(\log(n))^{1/4}\right)\)
Clearly
Define \(f_n : \N \to \C\) by
\begin{equation*}
f_n(k) = \left\{
\begin{array}{ll}
h(n)\cdot k^{2/3} & \quad \textnormal{if}\; n > 1 \land 0 < k \leq n \\
0 & \quad \textnormal{if}\; n = 1 \lor k > n 
\end{array}\right.
\end{equation*}
\begin{equation*}
h(n)\cdot\|f_n\|
  = \sum\nolimits_{k=2}^n k^{-2+2/3}\
  \leq \sum\nolimits_{k=2}^\infty k^{-4/3}
  \leq \int\nolimits_0^\infty x^{-4/3}\,dx
  = -1/(-4/3 + 1) = 3.
\end{equation*}
Thus \(\lim_{n\to\infty} \|f_n\| = 0\).
But
\begin{align*}
\lim_{n\to\infty} \|f_n^2\|
 &= \lim_{n\to\infty} \sum\nolimits_{k=1}^n (h(n))^2\cdot k^{-2+4/3}
   = \lim_{n\to\infty} h(n)^2\cdot \sum\nolimits_{k=1}^n k^{-2/3} \\
 & \geq \lim_{n\to\infty} \left(\log(n)\right)^{-1/2}
     \cdot  \sum\nolimits_{k=1}^\infty k^{-1}
   \geq \lim_{n\to\infty} \left(\log(n)\right)^{-1/2} \log(n) \\
 &= \lim_{n\to\infty} \left(\log(n)\right)^{1/2} = \infty.
\end{align*}

%%%%%%% 7
\begin{excopy}
Let \(C^2 = C^2([0, 1))\) be the space of all complex functions
  on \([0, 1]\) whose
second derivative is continuous. Choose \(a > 0\), \(b > 0\), and define
\begin{equation*}
\|f\| = \|f\|_\infty + a\|f'\|_\infty +  b\|f''\|_\infty +
\end{equation*}
Show that this makes \(C^2\) into a Banach space,
  for every choice of $a$, $b$, but that
the Banach algebra axioms hold
 if and only if \(2b \leq a^2\).
 (For necessity, consider $x$ and \(x^2\).)
\end{excopy}

Assume the defined \(\|\|\) is an algebra norm.
Let \(f(x)=x\). So \((f^2)'(x) = 2x\) and
\hbox{\((f^2)''(x) = 2\)}.
We need \(\|f\cdot f\| \leq \|f\|\cdot\|f\|\) to hold.
\begin{align*}
1 + a\cdot 2 + b\cdot 2 &\leq (1 + a\cdot 1 + b\cdot 0)^2 \\
\Rightarrow 2a + 2b + 1 &\leq (a + 1)^2 \\
\Rightarrow 2b &\leq a^2.
\end{align*}

Conversely, assume \(2b \leq a^2\).
Pick arbitrary \(f,g\in C^2\).
\begin{equation*}
\newcommand{\IN}[1]{\|{#1}\|_\infty}
\arraycolsep=1.4pt
\def\arraystretch{1.6}
\begin{array}{lcl}
\|fg\|
 &=& \IN{fg} + a\IN{f'g + fg'} +  b\IN{f''g + 2f'g' + fg''} \\
 &\leq&  \IN{f}\cdot\IN{g} +
         a\left(\IN{f'}\cdot\IN{g} + \IN{f}\cdot\IN{g'}\right) + \\
 &&      b\left(\IN{f''}\cdot\IN{g} + \IN{f}\cdot\IN{g''}\right) +
         2b\IN{f'}\cdot\IN{g'} \\
 &\leq& \IN{f}\cdot\IN{g} +
         a\left(\IN{f'}\cdot\IN{g} + \IN{f}\cdot\IN{g'}\right) + \\
 &&      b\left(\IN{f''}\cdot\IN{g} + \IN{f}\cdot\IN{g''}\right) +
         a^2\IN{f'}\cdot\IN{g'} \\
 &\leq& \IN{f}\cdot\IN{g} +
        a\left(\IN{f}\cdot\IN{g'} + \IN{f'}\cdot\IN{g}\right) + \\
 &&     b\left(\IN{f}\cdot\IN{g''} + \IN{f''}\cdot\IN{g}\right) +
        a^2\IN{f''}\IN{g''} +
        ab\IN{f'}\IN{g''} \\
 &=& (\IN{f} + a\IN{f'} +  b\IN{f''})
     \cdot
     (\IN{g} + a\IN{g'} +  b\IN{g''}) \\
 &=& \IN{f}\cdot\IN{g}.
\end{array}
\end{equation*}
So the inequality of norm required for algebra holds.

%%%%%%% 8
\begin{excopy}
What happens if the process of adjoining a unit (described in Section~10.1) is
applied to an algebra $A$ which already has a unit? Clearly,
  the result cannot be
an algebra $A$, with two units, Explain.
\end{excopy}

Following the Section~10.1 notation.
If the original algebra $A$ has a unit \(e_A\)
then it is mapped to \((e_A,0) \in A_1\)
which is \emph{not} a unit in \(A_1\).
For example:
\begin{equation*}
  (e_A,0)\cdot(0, 1) = (e_A,0) \neq (0, 1).
\end{equation*}

%%%%%%% 9
\begin{excopy}
Suppose that \(\Omega\) is open in \(\C\)
and that \(f: \Omega \to A\)
and \(\varphi: \Omega \to \C\) are holomorphic.
Prove that \(\varphi f : \Omega \to A\) is holomorphic.
[This was used in the proof of Theorem~10.13,
  with \(\phi(\lambda) = \lambda^n\).]
\end{excopy}

[See \cite{RudinPMA85} Theorem~5.3]
If \(\varphi f \) is holomorphic, then
\((\varphi f)' = \varphi'f + \varphi f'\).
Using the continuity of multiplication with scalar
\begin{align*}
 \lim_{w\to z} \frac{\varphi(w)f(w) - \varphi(z)f(z)}{w - z}
 &= \lim_{w\to z} \frac{
   \varphi(w)(f(w) - f(z)) + (\varphi(w) - \varphi(z))f(z)}{w - z} \\
 &= \left(\lim_{w\to z} \varphi(w)\frac{f(w) - f(z)}{w - z}\right) +
    \left(\lim_{w\to z} \frac{\varphi(w) - \varphi(z)}{w - z}\right)f(z) \\
 &= \varphi(z)f'(z) + \varphi'(z)+f(z).
\end{align*}
and the limits exist.

%%%%%%% 10
\begin{excopy}
Another proof that \(\sigma(x) \neq \emptyset\)
  can be based on Liouville’s theorem~3.32 and the
fact that \((\lambda e - x)^{-1} \to 0\) as \(\lambda \to \infty\).
  Complete the details.
\end{excopy}

If \(x = \lambda e\) for some \(\lambda \in C\) then
clearly this \(\lambda \in \sigma(x)\).

So we can assume that \(x \neq \lambda e\) for all  \(\lambda \in C\).
If by negation  \(\sigma(x) = \emptyset\) then
and \(f(\lambda) = ((\lambda e - x)^{-1}\) is entire holomorphic
function (using proof similar to that of Theorem~5.3 \cite{RudinPMA85}.
Clearly \(\lim_{\lambda\to\infty}f(\lambda) = 0\).
Hence there exists \(r>0\) such that \(|f(z)| < 1\) whenever \(|z|>r\)
and \(|f|\) achieves a maximum in the \(B(0,r)\) ball
and so $f$ is bounded. By Liouville’s theorem~3.32 $f$ is constant
which is a contrdiction (\(|f(0)| > 0\) and it vanishes at infinity).

%%%%%%% 11
\begin{excopy}
Call \(x \in A\) a \emph{topological divisor of zero}
if there is a sequence \(\{y_n\}\) in $A$, with
\(\|y_n\| = 1\), such that
\begin{equation*}
\lim_{n\to\infty} xy_n, = 0 = \lim_{n\to\infty} y_nx.
\end{equation*}
\begin{itemize}
\itemch{a}
Prove that every boundary point $x$
  of the set of all invertible elements of $A$ is
a topological divisor of zeroq.
  \emph{Hint:} Take \(y_n = x_n^{-1} /\|x_n^{-1}\|\), where \(x_n \to x\).
\itemch{b}
In which Banach algebras is $0$ the only topological divisor of $0$?
\end{itemize}
\end{excopy}

\begin{itemize}
\itemch{a}
  \newcommand{\limn}{\lim_{n\to\infty}}
  % using
  % mathonline.wikidot.com/boundary-points-of-inv-a-are-topological-divisors-of-zero-in
  If \(x=0\in A\) then it is trivially topological divisor of $0$.
  So we may assume \(x\neq 0\).
  Let \(G(A)\) be the group of invertible elements of $A$.
  By Theorem~10.11 \(G(A)\) is open, hence \(x\in \boundary{G(A)}\)
  is not invertible.
  Let \((x_n)_{n\in\N}\) be a sequence in \(G(A)\)
  such that \(\limn x_n = x\).

  Assume by negation \(\|x_n^{-1}\|\neq M < \infty\) is bounded.
  \begin{equation*}
  \|a_m^{-1} - a_n^{-1}\|
  = \|a_m^{-1}(a_n - a_m)a_n^{-1}\|
  \leq 2M\|a_n - a_m\|.
  \end{equation*}
  Since \((x_n)_{n\in\N}\) is a Cauchy sequence, so is \((x_n^{-1}\)
  that converges to \(y = \limn a_n^{-1}\) since $A$ is
  topologically complete. Since the multiplication is continuous,
  \begin{equation*}
  xy = \left(\limn x_n\right)\cdot\left(\lim nx_n\right)
  = \limn x_n\cdot x_n^{-1} = 1.
  \end{equation*}
  A contradiction to $X$ not being invertible.
  Thus  \((\|x_n^{-1})\|)\) not bounded.

  By moving to a subsequence  \((x_n)_{n\in\N}\),
  we may now assume that \(\|x_n^{-1}\| \geq n\).
  Let \(z_n = x_n^{-1}/\|x_n^{-1}\|\) so \(\|z_n\|=1\) for all \(n\in\N\).
  Now, from right
  \begin{align*}
  \limn \|xz_n\|
    &= \limn \|(x - x_n)z_n + x_n z_n\| \\
    &\leq \limn \|(x - x_n\| + \limn \|x_n \cdot x_n^{-1}/\|x_n{-1}\|
    = 0 + 0 = 0.
  \end{align*}
  And from left
  \begin{align*}
  \limn \|z_n x\|
    &= \limn \|z_n(x - x_n) + z_n x_n\| \\
    &\leq \limn \|x - x_n\| + \limn \|x_n^{-1} \cdot x_n/\|x_n{-1}\|
    = 0 + 0 = 0.
  \end{align*}
  Thus $x$ is a topological divisor of $0$.
\itemch{b}
  From Theorem~10.11 the invertible elements \(G(A)\) form an open set.
  From \ich{a} such algebras must have all its nonzero elements be invertible.
  Fron Theorem~10.14 these are isomorphic to \(\C\).
\end{itemize}

%%%%%%% 12
\begin{excopy}
Find the spectrum of the operator \(T \in \scrB(\ell^2)\) given by
\begin{equation*}
T(x_1,x_2,x_3,x_4,\ldots) = (-x_2,x_1,-x_4,x_3,\ldots).
\end{equation*}
\end{excopy}
It is sufficient to look on \((x_1,x_2)\)
and restrict $T$ to \(\C^2\). Thus $T$ can be represented as
\(\left(
\begin{smallmatrix}
0 & -1 \\
1 & 0
\end{smallmatrix}
\right)\). It characteristic polynomial is \(p_T(x) = x^2 + 1\)
whose roots are \(i\) and \(-i\).
Indeed \(T \pm iI\) are non invertible with two non trivial kernels.
One kernel
consisting of all \((-x_2,x_1,-x_4,x_3,\ldots)\)
such that \(x_{2n} = ix_{2n-1}\) for all \(n\in\N\).
A Similar kernel, such that \(x_{2n} = -ix_{2n-1}\) for all \(n\in\N\).
So \(\sigma(T) = \{i, -i\}\).

%%%%%%% 13
\begin{excopy}
Suppose \(K = \{\lambda \in \C: 1 \leq |\lambda| \leq 2\}\).
  Put \(f(\lambda) = \lambda\). Let $A$ be the smallest closed
subalgebra of \(C(K)\) that contains $1$ and $f$.
Let $B$ be the smallest closed sub-algebra
  of \(C(K)\) that contains $f$ and \(1/f\).
  Describe the spectra \(\sigma_A(f)\) and \(\sigma_B(f)\) .
\end{excopy}

If by negation \(1/f \in A\) then we can find polynomials \((p_n)_{n\in\N}\)
such that \(\lim_{n\to\infty} p(f) = 1/f\) on \(C(K)\).
But then on the unit circle path \(\gamma(t) = e^{2\pi i t}\)
we would have
\begin{equation*}
0 = \frac{1}{2\pi i}\int_{\gamma} (p_n(f))(\zeta)d\zeta
  = \lim_{n\to\infty}\frac{1}{2\pi i}\int_{\gamma} (p_n(f))(\zeta)d\zeta
  = \frac{1}{2\pi i}\int_{\gamma} d\zeta/f(\zeta) = 1.
\end{equation*}
Thus \(A \subsetneq B\).

Clearly \(K \subset \sigma_B(f) \subset \sigma_A(f)\).
As we saw above \(1/f \notin A\)
hence \(0 \in \sigma_A(f) \setminus \sigma_B(f)\).
Let \(z \in \{z \in \C: 0 < |z| < 1\}\), then
\begin{equation*}
(ze - f)^{-1}
= (ze - \lambda)^{-1}
= z^{-1}(e - z\lambda)^{-1}
= z^{-1}\sum_{n=0}^\infty (z\lambda)^n.
\end{equation*}
The last series converges iff \(|z\lambda| < 1\) for all \(\lambda \in K\).
Since in $K$, we can have \(|\lambda|=2\)
the series converges iff \(|z|<1/2\).

To summarize, \(\sigma_B(f) = \{z\in \C: 1/2 \leq |z| \leq 2\}\)
and  \(\sigma_A(f) = \sigma_B(f) \cup \{0\}\).

%%%%%%% 14
\begin{excopy}
\begin{itemize}
\itemch{a}
Fubini’s theorem was applied to vector-valued integrals in the proof of
Theorem~10.29. Justify this.
\itemch{b}
Construct a proof of Theorem~10.29 that uses no contour integrals, as
follows: Prove the theorem first for polynomials $g$, then for rational
  functions
  $g$ with no poles in \(\Omega\), and obtain the general case from Runge’s
  theorem.
\end{itemize}
\end{excopy}

Given \(x\in A_\Omega\), \(f\in H(\Omega)\),
open \(\Omega_1 \supset f(\sigma(x))\),
\(g\in H(\Omega_1)\)\\
and \(h(\lambda)=g(f(\lambda))\)
in \hbox{\(\Omega_0 = \{\lambda \in \Omega: f(\lambda) \in \Omega_1\}\)}.

\begin{itemize}
\itemch{a}
We have
\begin{equation*}
\tilde{f}(x)
  = \frac{1}{2\pi i}\int_{\Gamma_0} f(\lambda)(\lambda e - x)^{-1}\,d\lambda.
  \qquad (x\in A_{\Omega_0})
\end{equation*}
and
\begin{equation*}
\tilde{g}(y)
  = \frac{1}{2\pi i}\int_{\Gamma_1} g(\zeta)(\zeta e - y)^{-1}\,d\zeta.
  \qquad (y\in A_{\Omega_1})
\end{equation*}
For appropriate \(\Gamma\) contours.
We have
\begin{equation*}
\Ind_{\Gamma_1} (f(\lambda))
  = \frac{1}{2\pi i}\int_{\Gamma_1} \frac{dz}{z - \lambda}  = 1
\end{equation*}
Similarly
\begin{equation*}
g(f(\lambda)) =
\Ind_{\Gamma_1} g(f(\lambda))
  = \frac{1}{2\pi i}\int_{\Gamma_1} \frac{g(\zeta)}{\zeta - f(\lambda)}\,d\zeta
\end{equation*}
and using Theorem 10.27 we also have
\begin{equation*}
\left(\zeta e - \tilde{f}(x)\right)^{-1}
 = \frac{1}{2\pi i}\int_{\Gamma_0}
   (\zeta - f(\lambda))^{-1}(\lambda e - x)^{-1}\,d\lambda.
\end{equation*}
Thus
\begin{align}
\widetilde{g}\left(\widetilde{f}(x)\right)
  &= \frac{1}{2\pi i}\int_{\Gamma_1}
    g(\zeta)\left(\zeta e - \widetilde{f}(x)\right)^{-1}\,d\zeta \nonumber \\
  &= \frac{1}{2\pi i}\int_{\Gamma_1}
    g(\zeta)
      \left(
        \frac{1}{2\pi i}\int_{\Gamma_0}
          (\zeta - f(\lambda))^{-1}(\lambda e - x)^{-1}\,d\lambda
      \right)\,d\zeta \nonumber \\
  &= \frac{1}{(2\pi i)^2}  
    \int_{\Gamma_0}
      \left(
        \int_{\Gamma_1}
          g(\zeta)
          (\zeta - f(\lambda))^{-1}(\lambda e - x)^{-1}\,d\zeta
      \right)
      \,d\lambda  \label{eq:10.14:fubini} \\
  &= \frac{1}{(2\pi i)^2}
    \int_{\Gamma_0}
      \left(
        \int_{\Gamma_1}
          g(\zeta)
          (\zeta - f(\lambda))^{-1}\,d\zeta
      \right)
      (\lambda e - x)^{-1}
      \,d\lambda \nonumber \\
  &= \frac{1}{(2\pi i)} \int_{\Gamma_0} g(f(\lambda))(\lambda e - x)^{-1}\,d\lambda
    = \frac{1}{(2\pi i)} \int_{\Gamma_0} h(\lambda)(\lambda e - x)^{-1}\,d\lambda
      \nonumber \\
  &= \widetilde{h}(x) \nonumber.
\end{align}
The Fubini's theorem is applied in \eqref{eq:10.14:fubini}.
Both measures on \(\Gamma_0\) and \(\Gamma_1\) are finite.
\itemch{b}
Assume
\(g(x) = \sum_{p=0}^n a_p x^p\) s a polynomial. So
\begin{align}
\widetilde{g}\left(\widetilde{f}(x)\right)
  &= \frac{1}{2\pi i}\int_{\Gamma_1}
    g(\zeta)\left(\zeta e - \widetilde{f}(x)\right)^{-1}\,d\zeta \nonumber \\
  &=  \frac{1}{2\pi i}\int_{\Gamma_1}
        \sum_{p=0}^n
        a_p \zeta^p \left(\zeta e - \widetilde{f}(x)\right)^{-1}\,d\zeta
          \nonumber
   =  \sum_{p=0}^n
        a_p
        \frac{1}{2\pi i}
        \int_{\Gamma_1}
          \zeta^p \left(\zeta e - \widetilde{f}(x)\right)^{-1}\,d\zeta
            \nonumber \\
  &= \sum_{p=0}^n a_p \left(\widetilde{f}(x)\right)^p \label{eq:10.14b:poly} \\
  &= \sum_{p=0}^n a_p \widetilde{f^p}(x) \nonumber \\
  &= \sum_{p=0}^n a_p
    \frac{1}{2\pi i}
    \int_{\Gamma_0}
    (f(\lambda))^p(\lambda e - x)^{-1}\,d\lambda 
  = \frac{1}{2\pi i}\int_{\Gamma_0}
    \sum_{p=0}^n a_p(f(\lambda))^p(\lambda e - x)^{-1}\,d\lambda \nonumber \\
  &= \frac{1}{2\pi i}\int_{\Gamma_0} g(f(\lambda))(\lambda e - x)^{-1}\,d\lambda
    \nonumber \\
  &= \widetilde{(g\circ f)}(x) = \widetilde{h}(x) \nonumber
\end{align}
Equality (7) of section~10.13 gives \eqref{eq:10.14b:poly}.

Assume $g$ is of form \(g(\lambda) = (\lambda - \alpha)^{-k}\)
with integer \(k>0\) and where the pole \(\alpha\) is
outside
\(\Omega_1 \supset f(\sigma(x)) = \sigma\left(\widetilde{f}(x)\right)\).
\begin{align}
\widetilde{g}\left(\widetilde{f}(x)\right)
  &= \frac{1}{2\pi i}
     \int_{\Gamma_1}
       (\zeta - \alpha)^{-k}\left(\zeta e - \widetilde{f}(x)\right)^{-1}\,d\zeta
     \nonumber \\
  &= \frac{(-1)^k}{2\pi i}
     \int_{\Gamma_1}
       (\alpha - \zeta)^{-k}\left(\zeta e - \widetilde{f}(x)\right)^{-1}\,d\zeta
     \nonumber \\
  &= (-1)^k(\alpha e -  \widetilde{f}(x))^{-k} \label{eq:10.14b:lem:10.24} \\
  &= \frac{(-1)^k}{2\pi i}\int_{\Gamma_0}
    (\alpha - f(\lambda))^{-k}(\lambda e - x)^{-1}\,d\lambda \nonumber \\
  &= \frac{1}{2\pi i}\int_{\Gamma_0}
    (f(\lambda) - \alpha)^{-k}(\lambda e - x)^{-1}\,d\lambda \nonumber \\
  &= \widetilde{(g \circ f)}(x). \nonumber
\end{align}
Lemma~10.24 gives \eqref{eq:10.14b:lem:10.24}.

We saw that the desired equality
\(\widetilde{g}\left(\widetilde{f}(x)\right) = \widetilde{(g \circ f)}(x)\)
holds when $g$ is polynomial or of the form \((\lambda - \alpha)^{-k}\).
Using simple additive argument (as done in the polynomial case),
we deduce that the equality holds also for any rational function
with poles outside \(\Omega\).

Now let \(g\in H(\Omega\).
Using Runge's theorem we have sequence of rational functions \((g_n)_{n\in\N}\),
all with poles outside \(\Omega\) that converges uniformly
on the compact \(\Gamma_1\).
Now the desired equality is provided by Theorem~10.27.
\end{itemize}

%%%%%%% 15
\begin{excopy}
Suppose $X$ is a Banach space, \(T \in \scrB(X)\) is compact,
and \(\|T^n\| \geq 1\) for all \(n \geq 1\).
Prove that the point spectrum of $T$ is not empty.
\end{excopy}

By Theorem~10.13 the spectrum radius
\(\rho(T) = \lim_{n\to\infty} \|T^n\|^{1/n} \geq 0\).
Thus there is some \(\lambda \in \sigma(T)\setminus\{0\}\).
By Theorem~4.25\ich{b} \(\lambda\) is an eigenvalue of $T$,
so \(\lambda \in \sigma_p(T) \neq \emptyset\).

%%%%%%% 16
\begin{excopy}
Let \(X = C((0, 1)\) and define \(T \in \scrB(X)\) by
\begin{equation*}
(Tx)(x) = \int_0^s x(u)\,du \qquad (0\leq s\leq 1).
\end{equation*}

Show that \(\sigma_p(T) = \emptyset\).
Hence \(f(\sigma_p(T)) = \emptyset\) for every $f$, but if \(f\equiv 0\),
then \(\widetilde{f}(T) = 0\); hence:
\begin{equation*}
\sigma_p(\widetilde{f}(T) = \sigma_p(0) = \{0\} \neq \emptyset.
\end{equation*}
The extra hypotheses in \ich{c} and \ich{d} of Theorem~10.33 are thus needed.
\end{excopy}

Assume by negation \(f\in C([0,1])\) is a nonzero eigenvector of $T$
with eigenvalue \(\lambda\in \C\), that is \(Tf = \lambda f\).
Clearly \(Tf = \lambda f \not\equiv 0\), so clearly \(\lambda\neq 0\).
We also have \(\lambda f(0) = (Tf)(0) = 0\) and \((Tf)' = f\).

Let's solve the differentiall equation \(f'(x)=\lambda f(x)\)
Using tip from \cite{coddington1984theory}.
\begin{equation*}
0 = f'(x) - \lambda f(x) 
  = \exp(-\lambda x)\cdot(f'x() - \lambda f(x))
  = \frac{d}{dx} \left(\exp(-\lambda x)\cdot f(x)\right).
\end{equation*}
Therefore \(\exp(-\lambda x)\cdot f(x) = c\) for some constant $c$,
ans so \(f(x) = c \cdot \exp(\lambda x)\).
Now since \(f(0) = 0\) we get the contradiction \(f\equiv 0\).

%%%%%%% 17
\begin{excopy}
Suppose that the spectrum of some \(x \in A\) is not connected.
Prove that $A$ contains a nontrivial idempotent~$z$.
(This is defined in Exercise~2.)
Prove also that \(A = A_0 \oplus A_1\), where
\begin{equation*}
A_0 = \{x: zx=0\}, \qquad A_1 = \{x: zx=x\}.
\end{equation*}
\end{excopy}

See Corollary of Theorem~3.3 in \cite{wermer2013banach}
and Theorem~5.5.2 in \cite{hille1974functional}.

Assume \(\sigma(x) = K_1 \disjunion K_2\) where \(K_j\) are non-empty compact and disjoint, and let \(\Omega_j\) (where \(j=1,2\)) be disjoint regions
such that \(K_j\subset \Omega_j\)
and \(\Gamma\) be a contour surrounding
 \(\Omega = \Omega_1 \disjunion \Omega_2\).
\iffalse
such that
\begin{equation*}
\Ind_{\Gamma_j}(z) = \frac{1}{2\pi i} \int_{\Gamma_j} \frac{dw}{w - z} =
  \left\{
    \begin{array}{ll}
    1 & \quad z \in K_j \\
    0 & \quad z \notin \Omega_j
    \end{array}
  \right.    
\end{equation*}
\fi

Now for any \(f\in H(\Omega)\)
\begin{equation*}
\widetilde{f}(x) = \frac{1}{2\pi i}
  \int_{\Gamma}
    (\zeta e - x)^{-1}f(\zeta)\,d\zeta\,.
\end{equation*}
Put \(c_j = \chi_{\restriction \Omega_j}\)
% Since $f$  is holomorphic on \(\Omega = \Omega_1 \disjunion \Omega_2\)
% and put
and clearly \(c_1 + c_2 = \bm{1}_\Omega\).
Put
\begin{equation*}
z_j = \frac{1}{2\pi i} \int_{\Gamma} (\zeta e - x)^{-1} c_j(\zeta)\,d\zeta\
\qquad (j=1,2).
\end{equation*}
% so by Theorem~10.27
Since the mapping \(f\to\widetilde{f}\) as defined in Section~10.26
is algebra isomorphism (by Theorem~10.27) we have \(z_j^2 = z_j\)
and \(z_1 + z_2 = e\). %% _{\widetilde{H}(A_\Omega)}\).
% The value of \(\widetilde{f}(x)\) integral does not change if we enlarge
% \(\Omega\) thus we can vuew it as a mapping to the whole $A$.

Clealy this mapping maps the constant functions \(0_\Omega\) and \(1_\Omega\)
to \(0_{A_\Omega}\) and \(e_{A_\Omega}\) respectabley.
Again since this mapping is isomorphism, and $f$ is not constant,
it is mapped to a different element than either \(0_{A_\Omega}\) nor \(e_{A_\Omega}\).
Thus each \(z_j\) is a non-trivial idempotent.

Now let \(A_j = \{z_j w: w\in A\).
For each \(w\in A\) we have \(w = z_1 w + z_2 w\), thus \(A = A_1 + A_2\).
If \(w\in A_1 \cap A_2\) then
\(w = z_1 w_1 = z_2 w_2 \) for some \(w_1, w_2 \in A\) and
\begin{equation*}
w = ew = (z_1 + z_2)w
  = z_1z_1w_1 + z_2z_2w_2 =
  = z_1w_1 + z_2w_2 = w + w = 2w.
\end{equation*}
Hence \(w = 0\) and so \(A = A_0 \oplus A_1\).

%%%%%%% 18
\begin{excopy}
Suppose \(\Omega\) is open in \C, \(\alpha\) is an isolated boundary point
of \(\Omega\), \(f:Q\to X\) is
a~holomorphic $X$-valued function (where $X$ is some complex Banach space), and
there is a smallest nonnegative integer $n$ such that
\begin{equation*}
|\lambda - \alpha|^n \|f(\lambda\|
\end{equation*}
is bounded as \(\lambda \to \alpha\).
If \(n > 0\), then $f$ is said to have a pole of order $n$ at \(\alpha\).
\begin{itemize}
\itemch{a}
Suppose \(x \in A\) and \((\lambda e - x)^{-1}\)
has a pole at every point of \(\sigma(x)\). [Note that
this can happen only when \(\sigma(x)\) is a finite set.]
  Prove that there is a non-trivial polynomial $P$ such that \(P(x) = 0\).
\itemch{b}
As a special case of \ich{a},
assume \(\sigma(x) = \{0\}\) and \((\lambda e - x)^{-1}\) has a pole of order
$n$ at $0$. Prove that \(x^n = 0\).
\end{itemize}
\end{excopy}

If by negation there were infinite number of poles,
then there would be accumulation point $a$ of them in the compact \(\sigma(x)\).
But there could be no pole in $a$, since for any $n$
and for any neighborhood of $a$, 
the value \(|\lambda - a|^n \|f(\lambda\|\) would be infinite
for some other \(\alpha \in \sigma(x)\).

If  $X$ is a Banach space,
we define \(D(f)\) derivative of function \(f:\C\to X\) at \(z\in \C\)
\begin{equation*}
(Df)(z) = \lim_{\lambda \to z} \frac{f(\lambda) - f(z)}{\lambda - z}
\end{equation*}
if the limit exists.
We say the $f$ is holomorphic in region \(\Omega \subset \C\)
if it has a derivative in all points of \(\Omega\).

Now, being finite, \(\sigma(x) = \{\seq{\alpha}{m}\}\) and
\(\alpha_j\) is a pole of order \(n_j\) of \(R(\lambda,x)=(\lambda e - x)^{-1}\).
Then put \(P(x) = \Pi_{j=1}^m (x - \alpha_j)^{n_j}\).

So now \(P(x)R(\lambda,x)\) is holomorphic as a function of \(\lambda\)
in punctured neighborhoods \(\{z\in\C: 0 < |z - \alpha_j| < \delta\}\)
of the poles. The Theorem~10.20 in \cite{RudinRCA80}
\begin{quote}
\textbf{Theorem~10.20}
\textit{
Suppose \(f\in H(\Omega\setminus\{a\})\) and $f$ is bounded in \(D'(a;r)\)
for some \(r > 0\). Then $f$ has a removable singularity in $a$.
}
\end{quote}
can be easily
generalized to holomorphic functions with range of complex Banch space.
Thus \(Q(\lambda) = P(\lambda) R(\lambda,x)\) can be considered holomorphic.
Let \(N=\deg)(P)=\sum_j n_j \geq 1\).
We have \(\lim_{\lambda\to\infty} \|\lambda R(\lambda,x)\| = 1\)
and \(\lim_{\lambda\to\infty} \|\lambda^{-N} P(\lambda)\| = 1\).

Exercise~10.4 in \cite{RudinRCA80}
\begin{quote}
Suppose that $f$ is an entire function, and
\(|f(x)| \leq A + B|z|^k\)
for all $z$, where $A$, $B$, and $k$ are positive numbers.
Prove that $f$ must be a polynomial.
\end{quote}

By extending this exercise to $A$-valued function, we conclude that
\(Q(\lambda)\) is a polynomial.

So now we have a \emph{polynomial} equality:
\begin{equation*}
P(\lambda) = P(\lambda)R(\lambda,x)(\lambda e - x) = Q(x)(\lambda e - x)
\end{equation*}
We substitute \(\lambda\) with $x$ and we get \(P(x) = 0\).

%%%%%%% 19
\begin{excopy}
Let \(S_R\), be the right shift, acting on \(\ell^2\),
as in Exercise~2. Let \(\{c_n\}\) be a sequence of
complex numbers such that \(c_n \neq 0\) but \(c_n\to 0\) as \(n\to\infty\).
 Define \(M \in \scrB(\ell^2)\) by
\begin{equation*}
(Mf)(n) = c_n f(n) \qquad (n \geq 0).
\end{equation*}
and define \(T \in scrB(\ell^2)\) by \(T = MS_R\).
\begin{itemize}
\itemch{a} Compute \(\|T^m\|\), for \(m = 1,2,3,\ldots\).
\itemch{b} Show that \(\sigma(T) = \{0\}\).
\itemch{c} Show that $T$ has no eigenvalue.
  (Its point spectrum is therefore empty,
  although its spectrum consists of a single point!)
\itemch{d} Show that \((\lambda I - T)^{-1}\) does not have a pole at $0$.
\itemch{e} Show that $T$ is a compact operator.
\end{itemize}
\end{excopy}

\begin{itemize}
\itemch{a} For \(n \leq m\) we have \((T^m f)(n) = 0\),\\
  for \(n > m\)
  we have \((T^m f)(n) = \left(\Pi_{j=n-m}^n C_j\right)f(n-m-1)\).
\itemch{b} \((Tf)(0)\) thus $T$ is not invertible, and so \(0\in\sigma(T)\).
  Assume \(\lambda\in\sigma(x)\setminus\{0\}\), then
  \begin{equation*}
  ((\lambda e - T)(f))(n)
  = (\lambda f(1), \lambda f(2) - c_2 f(1), \lambda f(3) - c_3 f(2), \ldots,)
  \end{equation*}
  So
  \begin{align}
  \left((\lambda e - T)^{-1}(g)\right)(n)
  &= (g(1)/\lambda, (g(2) + c_2 f(1))/\lambda, (g(3) + c_3 f(2))/\lambda, \ldots)
  \notag \\
  &= g(1)/\lambda,
    c_2 g(1)/\lambda^2 g(2)/\lambda,
    c_2c_3 g(1)/\lambda^3 + c_3 g(2)/\lambda^2 + g(3)/\lambda, 
    \ldots) \label{eq:ex10.19b}
  \end{align}
  Thus \(\lambda \notin \sigma(T)\) and \(\sigma(T)=\{0\}\).
\itemch{c}
  \begin{equation*}
  (Tf)(n) = T(f(1),f(2),\ldots,) = (0, c_2f(1), c_2f(2), \ldots.)
  \end{equation*}
  If $f$ is an eigenvector, then \(f(1)=0\) and by induction \(f(n)=0\)
  for all \(n\in\N\). Thus \(f=0\) and there are no eigenvalues.
\itemch{d}
  From \eqref{eq:ex10.19b} we see that \((\lambda e - T)^{-1}\)
  has a term with \(\lambda^{-n}\) for any $n$.
  Thus there cannot be a pole of order $n$ that cancels all the terms
  to get a bounded value of \(\lambda^n (\lambda e - T)^{-1}\).
\itemch{e}
  We need to show that \(\overline{T(U)}\) is compact in \(\ell^2]\)
  where \(U=\{x\in \ell^2: \|x\|_2 < 1\}\).
  Let a sequence \(F_0\) in \(\overline{T(U)}\).
  Note that each element of \(F_0\) is in \(\ell^2\) a sequence itself.
  By induction we will build
  a sequence of sequences \(F_n\) in \(\overline{T(U)}\) such that
  We denote the sequence elements of \(F_n\) by \(f_{n,k}\)
  \begin{itemize}
  \item \(F_{n+1}\) is a subsequence of \(F_n\),
  \item \(\Lambda_k = \lim_{k\to\infty} f_{n,k}(k) \) exists within \(B(0,|c_k|)\)
        for each \(k \leq n\).
  \item \(|f_{n,m}(k) - \Lambda_k| < 2^{-k}\)
  \end{itemize}
  By induction, assume \(f_n\) are defined for for \(n\leq m\).
  Now the set of \(\{f_{m,k}(m)\} \subset B(0,|c_m|)\).
  This complex ball is compact, so we take as \(F_{m+1}\)
  a subsequence of \(F_m\) such that \(\{f_{m+1,k}(m)\}\) has a limit.
  and all the elements are within \(B(\Lambda_m,2^{-m})\).
  Now we take a ``diagonal'' subsequence $G$ such that \(G_k = f_{n,n}\).
  Now \(\lim_{p\to\infty} G_k(p)\) converges.
  Thus every sequence in \(\overline{T(U)}\) has a converging subsequence.
  Thus being closed in a metric space it is compact and so is $T$.
\end{itemize}

%%%%%%% 20
\begin{excopy}
Suppose \(x \in A\), \(x_n \in A\), and \(\lim x_n = x\).
  Suppose \(\Omega\) is an open set in \C\ that
contains a component of \(\sigma(x)\).
  Prove that \(\sigma(x_n)\) intersects \(\Omega\) for all sufficiently
large $n$. (This strengthens Theorem~10.20.) Hint:
  If \(\sigma(x) \subset \Omega \cup \Omega_0\), where \(\Omega_0\) is
an open set disjoint from \(\Omega\),
  consider the function $f$ that is $1$ in \(\Omega\), $0$ in \(\Omega_0\).
\end{excopy}
\unfinished

%%%%%%% 21
\begin{excopy}
Let \(C_R\), be the algebra of all real continuous functions on \([0, 1]\),
  with the
supremum norm. This satisfies all requirements of a Banach algebra, except that
the scalars are now real.
\begin{itemize}
\itemch{a} If \(\phi(f)) = \int_0^1 f(t)\,dt\), then \(\phi(1) = 1\),
  and \(\phi(f) \neq 0\) if $f$ is invertible in \(C_R\), but
  is not multiplicative.
\itemch{b} If $G$ and \(G_1\), are defined in \(C_R\) as, in Theorem~10.34,
  show that \(G/G_1\) is a
  group of order 2.
\end{itemize}
The analogues of Theorem~10.9 and \ich{d} of Theorem~10.34 are thus false
for real scalars. Exactly where would the proof of \ich{d} of Theorem~10.34
break down?
\end{excopy}
\unfinished

%%%%%%% nn
\begin{excopy}
\end{excopy}
\unfinished

%%%%%%%%%%%%%%%
\end{enumerate}
%%%%%%%%%%%%%%%
