\documentclass{book}

\input{mymacs}
\makeatletter
\@ifclassloaded{book}{
 \newcommand{\isbook}{Yes}
}{
 \newcommand{\isbook}{No}
}
\@ifclassloaded{article}{
 \newcommand{\isarticle}{Yes}
}{
 \newcommand{\isarticle}{No}
}

\makeatother

\newcommand{\upstar}{\raise.5ex\hbox{\(*\)}}
\newcommand{\unfinished}{\par\textbf{Unfinished !!!!!!!!!!!!!}\par}

\title{Weak-To-Weak}
\author{Yotam Medini}

\begin{document}

\maketitle


Here is a basic topological result.

See \cite{Megginson1998} Corollary~2.4.5
\begin{llem} \label{llem:cont:bymaps}
Let \((W,\tau)\) be a topological space and $X$ be a set topologized
by a a family \calF\ of mappings \(f: X \to Y_f\).
A mapping \(g:W\to X\) is continuous iff \(f\circ g\) is continuous
for all \(f\in\calF\).
\end{llem}
\begin{proof}
If $g$ is continuous then \(f\circ g\) are continuous simply
by composition of continuous mappings.

Conversely, we assume \(f\circ g\) is continuous for all \(f\in\calF\).
It will be sufficient to show that \(g^{-1}(B)\) is open in $W$
for any set $B$ in a basis for the topology of $X$.

Let $G$ be a family of inverse images of open sets \(f^{-1}(V)\)
where \(f\in\calF\) and $V$ is open in \(Y_f\).
Following  the discussion of Section~3.8
let the $S$ be the family that consists of finite intersections
of sets from $G$. It is a subbasis for 
the topology of $X$ which consists of unions of sets from $S$.

Pick an arbitrary set
'\(B = \cap_{j\in J} f_j^{-1}(V_j)\) from the subbasis $S$ where \(V_j\) is open 
in \(Y_{f_j}\) and $J$ is a finite set of \calF-indices.
% (The finiteness $J$ is actually not needed for our arguments).
Put \(U_j = f_j^{-1}(V_j) \subset X\).
By the assumption each \((f_j\circ g)^{-1}(V_j) = g^{-1}(U_j)\) 
is open in $W$.
It is easy to see that
\begin{equation*}
g^{-1}(B) = g^{-1}\left(\cap_{j\in J} U_j\right)
  = \cap_{j\in J} g^{-1}(U_j).
\end{equation*}
Hence \(g^{-1}(B) \in \tau\) and so $g$ is continuous.
\end{proof}


The relation between continuity and boundness
Will now be shown form normed spaces.
\begin{llem} \label{llem:op:cont:bounded}
Let \(T:X \to Y\) be a linear mapping between normed spaces.
Then $T$ is continuous iff \(T(E)\) is bounded in $Y$ whenever $E$
is bounded in $X$.
\end{llem}
\begin{proof}
Assume $T$ is continuous.
Let \(E\subset X\) be bounded subset.
Pick an arbitrary neighborhood \(0\in V \subset Y\)
By assumption there exists a neighborhood \(0 \in U \subset X\)
such that \(T(U) \subset V\) and there exists some \(n < 0\) such that
\(E \subset nU\). Hence 
\(T(E) \subset nT(U) \subset nV\). Hence the desired boundness condition 
holds for $T$. (Note that this direction did not use any norm).

Conversely, assume that $T$ maps bounded sets to bounded sets.
Then \(T(\{x\in X: \|x\| \leq 1\})\) is bounded in $Y$.
Thus there exists some \(M < \infty\) such that
\(\|Tx\| < M\) whenever \(\|x\| \leq 1\) where \(x \in X\).
Pick a neighborhood \(0\in V \subset Y\).
We can find some \(r > 0\) such that \(\{y\in Y: \|y\| \leq r\} \subset V\).
Put the open set \(W = \{x \in X: \|x\| < r/M\}\) and clearly
\(T(W) \subset U\). Thus $T$ is continuous at the origin.
By linearity $T$ is continuous.
\end{proof}


Here is a characterization of linear operator's boundness
(\cite{Megginson1998} Proposition~2.5.10).
\begin{llem}
Assume \(T:X \to Y\) is a linear operator between normed spaces.
Then $T$ is bounded  iff \(y^* \circ T \in X^*\) for all \(y^*\in Y^*\).
\end{llem}
\begin{proof}
If a functional is weakly-continuous then obviously it is
continuous in the norm topology. Theorem~3.10  gives the converse
that a any continuous functional is also weakly-continuous.
By Local-Lemma~\ref{llem:cont:bymaps} $T$ is weak-to-weak continuous.

The mapping $T$ is normed-continuous iff it \(T(E)\) is norm-bounded
in $Y$ whenever $E$ is normed bounded in $X$.
By Theorem~3.18 this is equivalent 
to the condition that \(T(E)\) is weakly-bounded
whenever $E$ weakly-bounded.
\end{proof}

The relation between operator continuity and its weak-continuity
is shown in the next result
\begin{llem} \label{llem:weak:to:weak}
Let \(T:X \to Y\) be a linear map between normed spaces.
Then $T$ is continuous iff $T$ is weak-to-weak continuous.
\end{llem}
\begin{proof}
By Local Leamm~\ref{llem:op:cont:bounded}
$T$ is continuous iff it map bounded sets to bounded sets.
By Theorem~3.18 it is equivalent to
require that $T$ maps weakly bounded sets to weakly bounded sets.
\end{proof}

Here a are simple lemmas regarding bounded and weak boundness of a set.
\begin{llem} \label{llem:bound:weakbound}
If $E$ is bounded then it is weakly bounded.
\end{llem}
\begin{proof}
Trivial since every weak neighborhood is a neighborhood
in the original topology.
\end{proof}


\begin{llem} \label{llem:bound:funcbound}
If  $E$ is a bounded subset of  a topological vector space $X$,
then \(\Lambda (E)\) is bounded in \C\ for every \(\Lambda \in X^*\).
\end{llem}
\begin{proof}
By  negation assume \(\Lambda(E)\) is unbounded.
Thus we can find a sequence \(x_n\in E\) such that \(|\Lambda x_n| \geq n\).
Define the open $0$ neighborhood \(V = \{x \in X: |\Lambda x\| < 1\}\).
Clearly \(x_n \notin nV\) for all $n$. Hence \(E \not\subset nV\) for all $n$
contradicting the assumption.
\end{proof}

We have a ``weak equivalnce''.
\begin{llem} \label{llem:weakbound:funcbound}
A subset  $E$ is weakly bounded in a topological vector space $X$,
iff \(\Lambda (E)\) is bounded in \C\ for every \(\Lambda \in X^*\).
\end{llem}
\begin{proof}
This was shown in the discussion of Section~3.11.
\end{proof}

With norm we have an equivalnce.
\begin{llem} \label{llem:bound:norm:funcbound}
Let  \(E \subset X\) where $X$ is a normed vector space.
Then $E$ is bounded iff \(\Lambda (E)\) is bounded in \C\ for
every \(\Lambda \in X^*\).
\end{llem}
\begin{proof}
If $E$ is bounded ,then it is weakly bounded and by
Local Lemma~\ref{llem:op:cont:bounded}
\(\Lambda (E)\) is bounded in \C\ for
every \(\Lambda \in X^*\).
Conversely, assume \(\Lambda (E)\) is bounded in \C\ for
every \(\Lambda \in X^*\). 
By Local Lemma~\ref{llem:weakbound:funcbound} again,
$E$ is weakly bounbded. By Theorem~3.18 it is also originally bounded.
\end{proof}

% Up to here - can be put in Chapter 3
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% To be put in Chapter 4

The following lemma shows that in boundness of operator
can be checked by looking at weak topologies, when the spaces are normed
(See \cite{Megginson1998} Proposition~2.5.11).
\begin{llem} \label{llem:op:normbd:weakbd}
Let \(T:X\to Y\) be a linear operator between normed spaces.
Then $T$ is bounded iff it is weak-to-weak bounded.
\end{llem}
\begin{proof}
Let \(B_X = \{x\in X: \|x\|\leq 1\}\).
By definitions, \(\Lambda\) is bounded if \(T(B_X)\) is bounded in $Y$. 
By Local Lemma~\ref{llem:bound:norm:funcbound} 
This is equivalent to  \((\Lambda T)(B_X)\) be bounded in \C\ for
all \(\Lambda \in Y^*\).
Since all these \(\Lambda T \in X^*\) for all \(\Lambda \in Y^*\)
the last condition means, that $T$ is bounded
iff  \((\Lambda T)(B_X)\) are continuous mappings \(X\to\C\)
for all \(\Lambda \in Y*\) considering the weak topology of $X$.

In turn, by Local Lemma~\ref{llem:cont:bymaps} this is equivalent 
to $T$ being continuous mapping 
from $X$ with its weak to $Y$ with its weak topology.
\end{proof}

\begin{center}
Now Back To the 2nd part to be inserted in the Exercises!!
\end{center}

Conversely, assume $S$ is 
continuous linear mapping of \((Y^*, \tau)\) into \((X^*, \sigma)\).
Let \(\psi_X\) and \(\psi_Y\) the isomorphisms of $X$ and $Y$
to their second duals.
Pick \(x\in X\). By composition \(\psi_X \circ S\) is weakly\upstar\ continuous
functional on~\(Y^*\). Hence \(\psi_X \circ S \in \psi_Y(Y)\).
Define
\begin{equation*}
Tx = \psi_Y^{-1}(\psi_X \circ S) \in Y.
\end{equation*}
The linearity of $T$ is clear. By definition it is weak-to-weak continuous.
By local lemma~\ref{???} $T$ is also normed-continuous.
\end{document}
