%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapterTypeout{II. Infinitary combinatorics}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Notes}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Theorem 1.3}

In the proof of Theorem~1.3
\begin{equation*}
  A_X = \{X\cap \alpha: \alpha<\kappa\}.
\end{equation*}
It claims: If \(|X|=\kappa\) then \(|A_X|=\kappa\). Why?\\
For each distinct \(\alpha,\beta < \kappa\)
we \emph{cannot} simply show \(X\cap \alpha \neq X\cap\beta\), since
if we pick \(X' = X \setminus (\alpha \cup \beta)\)
we still have \(|X'|=\kappa\) but
\(X' = X'\cap \alpha = X' \cap \beta\).

We enumerate \(X=\{x_\beta: \beta < \kappa\}\).
For each \(\beta < \kappa\), we have \(\{x\in X: x< x_\beta\} = X\cap \alpha\)
for some \(\alpha\) (not necessarily unique \(\alpha\) for \(\beta\).
So the families:
\begin{itemize}
\item \(\{x\in X: x< x_\beta\}\) for each \(\beta < \kappa\)
\item \(X\cap \alpha\) for each \(\alpha < \kappa\)
\end{itemize}
are the same, and so \(|X|=\kappa\).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Theorem 1.6}

\iffalse
\begin{quote}
1.6. THEOREM. 
Let \(\kappa\) be any infinite cardinal. 
Let \(\theta > \kappa\) be regular and satisfy
\(\forall \alpha < \theta (|\alpha^{-\kappa}| < \theta\).
Assume \(|A| \geq \theta\) and \(\forall x\in A (|x|<\kappa)\),
then there is a
\(B \subset A\), such that \(|B| = \theta\) and $B$ forms a \(\Delta\)-system,
namely \(\exists r, \forall x,y\in B (x\neq y \implies x\cap y = r\).

Proof. By shrinking $A$ if necessary, we may assume \(|A| = \theta\). Then
\(|\cup A| \leq \theta\). Since what the elements of $A$ are as individuals
is irrelevant, we
may assume \(\cup A \subset \theta\). 
  Then each \(x \in A\)/ has some order type \(<\kappa\) as a subset
of \(\theta\), Since \(\theta\) is regular and \(\theta > \kappa\), 
  there is some \(\rho < \kappa\), such that 
\(A_1 = \{x\in A: x \;\textnormal{has type}\; \rho\}\) has cardinality \(\theta\). 
  We now fix such a \(\rho\) and deal only with \(A_1\)

For each \(a <\theta\), \(|\alpha^{<\kappa}| < \theta\)
  implies that less than \(\theta\) elements of \(A_1\) are
subsets of \(\alpha\).
  Thus, \(\cup A_1\) is unbounded in \(\theta\). 
If \(x\in A_1\) and \(\xi < \rho\), let \(x(\xi)\)
be the \(\xi\)-th element of $x$. 
  Since \(\theta\) is regular, there is some \(\xi\) such that
\(\{x(\xi): x\in A_1\}\) is unbounded in \(\theta\). 
  Now fix \(\xi_0\) to be the least such \(\xi\) 
  (\(\xi_0\) may be $0$). Let
\begin{equation*}
\alpha_0  = \sup\{x(\eta) + 1: x\in A_1 \land \eta < \xi_o\};
\end{equation*}
then \(\alpha_0 < \theta\) and \(x(\eta) < \alpha_0\) 
  for all \(x \in A_1\) and all \(n < \xi_0\).
By transfinite recursion on \(\mu < \theta\),
  pick \(x_\mu \in A_1\) sO that \(x_\mu(\xi_0) > \alpha_0\) and
\(x_\mu(\xi_0)\) is above all elements of earlier \(x_\nu\); i.e.
\begin{equation*}
X_\mu(\xi_0) > \max(\alpha_0, \sup \{x_\nu(\eta): \eta<\rho \land \nu<\mu\}).
\end{equation*}
Let \(A_2 = \{x_\mu: \mu < \theta\}\). 
  Then \(|A_2| = \theta\) and \(x\cap y \subset \alpha_0\) whenever $x$ and $y$
are distinct elements of \(A_2\). Since \(|\alpha*{<\kappa}| < \theta\), 
  there is an \(r\subset \alpha_0\) and a
\(B \subset A_2\)of, with \(|B| = \theta\) 
  and \(\forall x \in B (x \cap \alpha_0 = r)\),
  whence $B$ forms a \(\Delta\)-system with root $r$.
\end{quote}
\fi

In the proof of Theorem~1.6 it says:
\begin{quote}
Since \(\theta\) is regular and \(\theta > \kappa\), 
there is some \(\rho < \kappa\), such that
 \(\scrA_1 = \{x\in\scrA: x \;\textnormal{has type}\; \rho\}\)
has cardinality \(\theta\).
\end{quote}
To Justify:
\begin{equation*}
\scrA = \mathsmaller{\Disjunion_{\rho<\kappa}} 
  \{x\in\scrA: x \;\textnormal{has type}\; \rho\}.
\end{equation*}

In the proof of Theorem~1.6 it also says:
\begin{quote}
For each \(\alpha < \theta\), \(|\alpha^{<\kappa}| < \theta\)
implies that less than \(\theta\) elements of \(\scrA_1\) are
subsets of \(\alpha\) Thus, \(\cup \scrA_1\) is unbounded in \(\theta\).
\end{quote}
Estimatiom of subsets is justified by:
\begin{equation*}
\left|\alpha^{<\kappa}\right| 
  = \left|\cup_{\gamma<\kappa}\alpha^\gamma\right|
  \geq \left|\cup_{\gamma<\min(\alpha,\kappa)}\alpha^\gamma\right|
  \geq \left|\cup_{\gamma<\min\alpha,\kappa)} 
    \{\rng(f): f\in \alpha^\gamma\}\right|
  = \left|\{\alpha': \alpha'\subseteq \alpha\}\right|.
\end{equation*}
It is bounded, since \(\theta\) is a limit ordinal, 
\(|\cup \scrA_1|=\theta\) and \(\forall x\in\scrA (|x|<\theta\).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Exercises}

%%%%%%%%%%%%%%%%%
\begin{enumerate}
%%%%%%%%%%%%%%%%%

%%%%%%% 1
\begin{excopy}
Prove the \(\Delta\)-system lemma (1.5) directly. 
\emph{Hint}. One may assume that for
some $n$, \(\forall x \in \scrA (|x| =n)\). 
Now proceed by induction on $n$. Observe that
there is an uncountable \(\scrB \subset \scrA\) such that either 
\(\cap \scrB \neq \emptyset\) or \scrB\ is pairwise
disjoint.
\end{excopy}

The Theorem~1.5 says:
\begin{quote}
If \scrA\ is any uncountable family of finite sets, there is an uncountable
\(\scrB \subset \scrA\) which forms a \(\Delta\)-system.
\end{quote}
Put \(\scrA_n = \{A \in \scrA: |A|=n\}\).
Now the must exists some $n$ such that \(\scrA_n\) is uncountable.

Assume \(n=1\). Then take \(\scrB = \scrA_1\) 
and for each distinct \(B_1,B_2 \in scrB\), \(B_1\cap B_2 = \emptyset\)
thus \scrB\ is \(\Delta\)-system.

Induction step.
Assume that if all sets in \scrA\ are of the same size $s$ and \(s<n\)
then there exists \(\scrB_s\subset \scrA\) which is \(\Delta\)-system.
and assumee now that \(\scrA_n\) is uncountable.
Put \(R = \cup \scrA_n\) and well-order $R$.

\unfinished


\end{enumerate}
