\documentclass[11pt,pdftex,twoside,a4paper]{article}
\usepackage{amsthm}
\usepackage{array}
\usepackage{dsfont}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{relsize}

\input{mymacs}

\newcommand{\B}[1]{\textbf{#1}}
\newcommand{\Cohen}{\mathop{\rm Cohen}\nolimits}
\newcommand{\MA}{\ensuremath{\mathop{\rm MA}\nolimits}}
\newcommand{\ccc}{c.c.c.}
\newcommand{\CH}{\ensuremath{\mathop{\rm CH}\nolimits}}
\newcommand{\dsP}{\ensuremath{\mathds{P}}}
\newcommand{\crotin}{\rotatebox[origin=c]{-90}{\(\in\)}}
\newcommand{\finitepartial}{\textnormal{finite partial}}
\newcommand{\GCH}{\ensuremath{\mathop{\rm GCH}\nolimits}}
\newcommand{\Lev}{\ensuremath{\mathop{\rm Lev}\nolimits}}
\newcommand{\On}{\ensuremath{\mathit{On}}}
\newcommand{\otp}{\ensuremath{\mathop{\rm otpo}\nolimits}}
\newcommand{\rotin}{\rotatebox[origin=c]{90}{\(\in\)}}
\newcommand{\SH}{\ensuremath{\mathop{\rm SH}\nolimits}}
\newcommand{\Suc}{\ensuremath{\mathop{\rm Suc}\nolimits}}
\newcommand{\TC}{\ensuremath{\mathop{\rm TC}\nolimits}}
\newcommand{\tht}{\ensuremath{\mathop{\rm ht}\nolimits}}
\newcommand{\unfinished}{\par\textbf{Unfinished !!!!!!!!!!!!}\par}
\newcommand{\ZF}{\ensuremath{\mathop{\rm ZF}\nolimits}}
\newcommand{\ZFC}{\ensuremath{\mathop{\rm ZFC}\nolimits}}

\newtheorem{thm}{Theorem}[section]
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{claim}[thm]{Claim}
\newtheorem{corollary}[thm]{Corollary}
\theoremstyle{definition}
\newtheorem{ldef}[thm]{Definition}

\title{Advanced Set Theory 2
          \\
       Lecture Notes --- Professor Mordechai Gitik}

\author{Yotam Medini}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\maketitle
\newpage
\tableofcontents
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{2026/April/12}

In this course we will deal with independence of set theory axioms
Mainly with forcing methods introduced by Paul Cohen (1963).
Notably independence of the continuum hypothesis.

Text books for the course:
\begin{itemize}
  \item \B{Kunen} / \textit{SET THEORY,
    An Introduction to Independence Proofs}
  \item \B{Jech} / \textit{Set Theory}
\end{itemize}

The forcing technique facilitate other independency results.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Axioms System --- ZFC}

We introduce a generally accepted, Zermelo-Fraenkel and Choice
(ZFC) system of axioms.

\begin{enumerate}

\item (\B{Extensionality}) If $X$ and $Y$ has the same elements then \(X=Y\).

\item (\B{Pairing}) If $X$ and $Y$ are sets, then there is a set \((X, Y)\).
Cab be built as \(\{X\}, \{X,Y\}\}\).

\item (\B{Separation Scheme}) For any set $X$, the elements of $X$
that satisfy some attribute make a set.
Formally, for any formula \(\phi(x)\)
made of ($=$, $\in$, \(\neg\), \(\exists\), \(\rightarrow\)), then
\(\{x\in X | \phi(x)\}\) is a set.
Also called \B{Comprehension Scheme}.

\item (\B{Union}) For any set $X$, \(\cup X = \cup \{x|x\in X\}\) is a set.

\item (\B{Power}) For any set $X$, then \(\{Y| T\subseteq X\}\) is set.

\item (\B{Infinity})
  \(\exists X, \emptyset\in S, \forall x\in S (x\cup \{x\} \in S\).

\item (\B{Replacement Scheme}) An image of a set by a function is a set.
  Formally, let \(\phi(v,u)\) a formula
such that \(\forall v\exists!u\, \phi(v,u)\) then for any set $A$
there exists a set $B$ such that
 \(\forall v\in A \,\exists u\in B\, \phi(v,u)\).
To get an ``exact'' image we can use the separation axiom.

\item (\B{Regularity}) Any non-empty set $S$ has \(\in\)-minimal element.\\
Formally \(S\neq \emptyset \,\implies\, \exists x\in S\, x\cap S=\emptyset\).
\\
This Regularity axiom will be essential in our later development.
Also called \B{Foundation} or \B{Separation}.

\item (\B{Choice} --- \B{AC}) For any set $X$ (of sets)
\begin{equation*}
\left(\emptyset\notin X \,\land\,
  \forall x,y\in X x=y\lor x\cap y=\emptyset\right)
\implies
 \exists C, \forall x\in X\,\exists!y\, y\in C\cap x.
\end{equation*}
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Separation and Classes}

Given a formula \(\phi\) we can refer to the class \(\{x|\phi(x)\}\).
``Intersection'' of a set with a class is a set.

Say we a formula \(\phi(\seq{v}{n},\seq{u}{k}\)
and sets \seq{a}{k} we can form
\begin{equation*}
 \{(\seq{x}{n}\,|\,\phi(\seq{x}{n},\seq{a}{k})\}.
\end{equation*}
and later by pairing get a set.

\begin{claim}
For any class $C$ if \(C\neq\emptyset\) then there exists \(a\in C\)
such that \(a\cap C=\emptyset\).
\end{claim}
This is a generalization of the regularity axiom.
\begin{proof}
Let \(S\in C\), an element of a class must be a set.
Let \(A = S\cap C\). If \(A=\emptyset\) we are done.
Otherwise, \(A\neq \emptyset\) and we take \(\TC(A)\)
the \B{transitive closure} of $A$ as follows:
\begin{align*}
A_0 &= A\\
A_1 &= A_0 \cup (\cup A_0) \\
A_{n+1} &= A_n \cup (\cup A_n) \\
\TC(A) &= \bigcup_{n<\omega} A_n.
\end{align*}
\(\TC(A)\) is a set. This is the minimal set that contains $A$.
Put \(X = \TC(A)\). Now \(X \cap C \supseteq A \neq \emptyset\).

By regularity there exists \(x\in\ X \cap C\)
which is \(\in\)-minimal. We will show \(x\in C\), that is
\(x \cap (X\cap C)=\emptyset\). We will show that also
\(x \cap C=\emptyset\). By negation, there exists \(y \in x \cap C\).
So \(y\in x \in \TC(A)\). By transitivity \(y\in \TC(A)\),
this \(y \in X \cap C\), contradiction to minimality of $x$.
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%4
\subsection{Hierarchy}

Let us define the following hierarchy.
\begin{align*}
V_0 &= \emptyset \\
V_{\alpha+1} &= \mathds{P}(V_\alpha) \qquad\textnormal{power set} \\
V_\alpha &= \bigcup_{\beta<\alpha} V_\beta
  \qquad \alpha\ \textit{is a limit ordinal} \\
W &= \bigcup_{\alpha \in \On} V_\alpha.
\end{align*}

\begin{thm}
The regularity axiom implies \(V=W\) where $V$ is the world of sets.
\end{thm}
\begin{proof}
Assume regularity axiom, we will show \(V=W\).
By negation, let \(C = V \setminus W\neq \emptyset\)
There exists a set \(X \in C\) such that \(X \cap C = \emptyset\).
Thus \(\forall x\in X\, x\in W\) and so \(x \subseteq W\) and
there exists and \(\alpha\in \On\) such that \(X\subseteq V_\alpha\).
Thus \(x\in V_{\alpha+1} \subseteq W\) a contradiction.

Assume \(V=W\). For each set $X$ we define \(\rank(X)\)
the minimal ordinal \(\alpha\) such that \(X\in V_{\alpha+1}\).
\\
\B{Claim}: For any \(\alpha,\beta\in\On\):
\begin{enumerate}
\item \(V_\alpha\) is transitive.
\item \(\alpha < \beta \;\implies\; V_\alpha \subset V_\beta\).
\item \(x\in y\;\implies\; \rank(x) < \rank(y)\).
\item \(\rank(\alpha) = \alpha\).
\end{enumerate}
The claim can be easily proved by induction.

Using the claim, let $S$ be a non-empty set.
Pick \(x\in S\) having the minimal rank.
By negation, consider \(y \in x \cap S\).
Then \(\rank(y)<\rank(x)\), a contradiction.
\end{proof}

we conclude:
\begin{thm}
$W$ satisfies \(\textnormal{ZF} \setminus \textnormal{regularity}\).
\(W \;\models\; (\textnormal{ZF} \setminus \textnormal{regularity})\).
\end{thm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Forcing Methods}

Say we have a formula \(\phi\) in the language of set-theory.
What does: \(\;\textnormal{ZFC}\,\vdash\,\phi\;\) means?

It means that we have a sequence \(\seqn{\psi}{n}\) of claims,
such that each \(\psi_i\) is derived from ZFC or preceding claims
and \(\psi_n = \phi\).
So we need just a finite number of axioms from ZFC.

For example, if \(\ZFC \models \CH\),
then there is a \emph{finite} \(\ZFC' \models \CH\).

Later, we will use a countable transitive model $M$ of ZFC,
(or a finite sufficiently large subset of ZFC).
In this context, the reflection theorem
Mostowski Collapse Theorem, and G\"odel incomplete theorem were mentioned.

Then for any countable transitive model $M$ of ZFC', \(M \models \CH\).
We will want to contradict this by extend $M$ to \(M^*\)
still modeling \(\ZFC'\) but \(M^*\, \models \,\neg\CH\).

Let
\(\lrangle{\dsP,\leq_\dsP,0_\dsP}\)
also abbreviated by
\(\lrangle{\dsP,\leq,0}\)
be a partially ordered set
where \(0_\dsP\) is the smallest, \(\forall p\in\dsP\,(0_\dsP \leq_\dsP p)\)
is called \B{forcing notion}.
\\
Note: in the books of Kunen and Jech use opposite terms,
like the largest  \(1_\dsP\).

From now on, we asssume $M$ is a countable transitive model for ZFC
or a sufficiently large finite subset of ZFC.

For \(p,q\in\dsP\) We will say that $p$ is \emph{stronger} than $q$
or $q$ is weaker than $p$ iff  \(q \leq p\).

\begin{ldef}
Let \(p,q\in\dsP\). $p$ and $q$ are \emph{compatible} iff
\(\exists r\in\dsP\,(p,q\leq r)\).
\end{ldef}

\begin{ldef}
A set \(D\subseteq \dsP\) is \emph{dense} iff
\(\forall q\in\dsP\,\exists p\in\dsP\, q\leq p\).
\end{ldef}

\begin{ldef}
A set \(G\subseteq\dsP\) is called \emph{generic} iff
\begin{enumerate}
\item \(\forall p\in G\,(q\leq p\,\implies\,q\in G)\).
\item \(\forall p,q\in G\,\exists r\in G\, p,q\leq r\).
  That is compatible by element in $G$.
\item For any dense \(D\subseteq \dsP\),
  suh that \(D\in M\) and \(G\cap D\neq \emptyset\).
  % \label{item:generic:dense}.
\end{enumerate}
\end{ldef}

\begin{claim}
Let \(\lrangle{\dsP,\leq,0}\in M\) and \(p\in\dsP\)
then there exists a generic \(G\subseteq \dsP\) such that \(p\in G\).
\end{claim}
\begin{proof}
\(|M|=\aleph_0\). So there are countable number of dense sets
\(\{D_n|n<\omega\}\). Pick \(p_0\in D_0\) such that \(p \leq p_0\).
By induction, pick \(p_{n+1}\in D_{n+1}\) such that \(p_n \leq p_{n+1}\).
Let \(G=\{q\in\dsP|\exists n\, q \leq p_n\}\).
Clearly, $G$ satisfies the generic requirements
% but we need to show that \(G\in M\). ???
\end{proof}

\begin{ldef}
A partially ordere set \(\lrangle{\dsP,\leq}\) is called \emph{splitting}
If for any \(p\in\dsP\) there exists \(p_1\),\(p_2\) such that
\(p\leq p_1,p_2\) and \(p_1\),\(p_2\) are not compatible.
\end{ldef}

\begin{claim}
If \(\lrangle{\dsP,\leq,0}\) is splitting,
then each generic \(G\subseteq \dsP\),
\(G\notin M\).
\end{claim}
\begin{proof}
Let \(D = \dsP\setminus G\). We will show that $D$ is dense.
For each \(p\in\dsP\) there exists non-compatible \(p_1,p_2\in\dsP\).
So \(p_i\notin G\) for at least some \(i\in\{1,2\}\).
We can assume \(p\leq p_1 \in D\), thus $D$ is dense.
If by negation\(G\in M\) so is \(D\in M\),
but gives a contradiction since \(D\cap G=\emptyset\).
\end{proof}
Comment: If the order is linear, generic set must be everything.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Examples}
We look at partial finite functions
\begin{equation*}
C = \{f\,|\, f:\omega\to 2\,\land\,|\dom f|<\aleph_0\}.
\end{equation*}
with $f$ \emph{continues} $g$
\begin{equation*}
g \leq f \; \Leftrightarrow \; g \subseteq f.
\end{equation*}

Let \(\lrangle{C,\leq,0}\) be a forcing notion
--- Real-Cohen-forcing.
The set
\begin{equation*}
D_n = \{f\in C|\, n\in \dom(f)\}\qquad n < \omega
\end{equation*}
is dense. Let \(h\in C\). If \(n\in \dom(h)\) then \(h\in D_n\).
Otherwise \(h' = h\cup\{(n,0)\} \in D_n\).

Let \(G\subseteq C\) generic and let \(g = \cup G\).
Then $g$ is parial function \(\omega \to 2\).
Actually $G$ is a total function, since \(G\cap D_n\) for each \(n<\omega\).
But \(g\notin M\), since if by negation \(h:\omega\to w\) and \(h\in M\),
then
\begin{equation*}
D^h = \{f\in C|\, \exists n\in \dom(f)\, f(n)\neq h(n)\}
\end{equation*}
We show that \(D^h\) is dense.
Let \(\tilde{f} \in C\). Pick sufficiently large \(n<\omega\)
such that \(n\notin\dom(\tilde{f})\) and define
\(f = \tilde{f}\cup \{(n, 1 - h(n))\}\).
So \(G\cap D^h \neq \emptyset\).
By negatiom, we take \(h=g\in M\). 
Pick some \(p\in (G\cap D^h\).
\(p\in G\) so 
\(p\forall n\in \dom(p)\, p(n)=g(n)\)
but \(p\in D^h\) so 
\(p\forall n\in \dom(p)\, p(n)\neq h(n)=g(n)\)
a contradiction.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{An Advanced Example}

We present a more advanced example in $M$.
Let \(\lambda \leq \aleph_2\). Define
\begin{equation*}
C(\lambda) = \{f|\, f:\lambda\times\omega\to 2 \,\wedge\, |\dom(f)|<\aleph_0\}.
\end{equation*}
With similar order: 
\(\tilde{f}\leq f \,\Leftrightarrow\, \tilde{f} \subseteq f\).
Let \(G \subseteq C(\lambda\) be generic.
Let \(\alpha < \lambda\). Put
\begin{align*}
D_\alpha &= \{f\in C(\lambda)|\, \exists n<\omega\, (\alpha,n)\in \dom(f)\} \\
D_{\alpha,n} &= \{f\in C(\lambda)|\, (\alpha,n)\in \dom(f)\}
\end{align*}
For any \(\alpha<\lambda\) and \(n<\omega\) \(D_{\alpha,n}\) is dense
\(G\cap D_{\alpha,n} \neq \emptyset\).
Let \(g = \cup G\). For each \(\alpha<\lambda\) 
define \(g_\alpha:\omega\to 2\) by \(g_\alpha(n) = g(\alpha,n)\).

Assume \(\alpha,\beta<\lambda\) and \(\alpha\neq\beta\), then
\begin{equation*}
D^{\alpha,\beta} = \{f |\,\exists n<\omega\,(f(\alpha,n)\neq f(\beta,n))\}
\end{equation*}
is dense \(G\cap D^{\alpha,\beta} \neq \emptyset\)
and \(g_\alpha \neq g_\beta\).

The idea is later to add $G$ to $M$, and destroy \CH.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\(\aleph_2\) in $M$}

In $M$ \(\aleph_2\) can become countable.

Again, let \(\lambda \leq \aleph_2\). Define
\begin{equation*}
\textnormal{Col}(\omega,\lambda) 
  = \{f|\, f: S\to\lambda \wedge S\subset\omega\ \wedge \dom(f)<\aleph_0\}.
\end{equation*}
Take \(G\subseteq \textnormal{Col}(\omega,\lambda)\) generic,
and \(g = \cup G\) and onto \(g:\twoheadrightarrow \lambda\).
This shows that \(\lambda\) becomes countable.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extending Model}

Let \(\lrangle{\dsP,\leq_\dsP,0_\dsP}\) be a forcing notion in $M$.
We build in $M$ a class \(M^\dsP\) of \emph{name}s by \dsP.
\begin{enumerate}
\item \(\emptyset\) is a name.
\item \(\tau\) is a name in \(M^\dsP\) if and element of \(\tau\)
   is an ordered pair \((\sigma,p)\) where \(\sigma\) is a name and
  \(p\in \tau\). This is seems like a cyclic definition, but
  \(\rank(\sigma)<\rank(\tau\) so we have recursion on reducing ranks.
\end{enumerate}

Let \(G\subseteq \dsP\) generic. For each \dsP-name (element in \(M^\dsP\))
\(\tau\) we define \emph{interpretation} of \(\tau\) 
\begin{equation*}
\tau_G = \{\tau_G|\,\exists p\in G (\sigma.p)\in \tau\}.
\end{equation*}
This is a recursive definition.

We define generic extension
\begin{equation*}
M[G] = \{\tau_h|\, \tau\in M^\dsP\}.
\end{equation*}

We will use \(M[G]\) to show negation of \CH\ and more.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{2026/April/19}

Let $M$ be a countable transitive model of ZFC,
or a sufficiently large subset of ZFC.
In $M$ a forcing notion \(\lrangle{\dsP,\leq_\dsP,0_\dsP}\),
witg \(\leq_\dsP\) a partial order or pre-partial order,
\(0_\dsP\) the smallest.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\dsP-names}

We define a class of \dsP-names \(M^\dsP\).

\begin{ldef}
\(\tau\in M^\dsP\) is a \dsP-\emph{name} if every element of \(\tau\)
is an ordered pair \(\sigma,p)\) such that \(\sigma\) is a \dsP-name
and \(p\in\dsP\) and \(\rank(p)<\rank(\tau)\).
\end{ldef}
This is a recursive definition with decreasing ranks.
\(M^\dsP\) is a class in $M$.
Names a are tools to refer to sets that are not in $M$.

\subsection{Genric Set}

\begin{ldef}
A set \(G\subseteq\dsP\) is \emph{Generic} iff
\begin{enumerate}
\item \(\forall p\in G\ \forall q\,(q\leq p \,\implies\, q\in G\).
\item \(\forall p,q\in G\,\exists r\in G\, p,q\leq r\).
\item For any dense set 
  \(D\subseteq \dsP\) (where \(D\in M\))  \(G\cap D\neq\emptyset\).
\end{enumerate}
\end{ldef}

\subsection{Reminders from previous lecture.}

In most interesting cases, generic sets are not in $M$.
\begin{claim}
Let \(\lrangle{\dsP,\leq}\) be a splitting order, and \(G\subseteq \dsP\)
generic, then \(G\notin M\).
\end{claim}

\begin{claim}
For any \(p\in\dsP\) there exists a generic $G$, such that \(p\in G\).
\end{claim}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Generic Extension}

Let \(G\subseteq M\) be generic.
We will define \(M[G]\) a \emph{generic extension} of $M$
We start wih \emph{names interpretations}

\begin{ldef}
Let \(G\subseteq M\) be generic for \(\lrangle{\dsP,\leq,0}\).
Let \(\tau\) be name, its \emph{interpretation by} $G$,
denoted by \(\tau_G\) (not a standard notation) is
\begin{equation*}
\tau_G = \{\sigma_G|\, \exists p\in G\, (\sigma,p)\in \tau\}.
\end{equation*}
\end{ldef}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
